An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/learner.tex
add table for anomalies
more accurate Hampel

\para{Learning from an incorrect set.}
The first step of \app is to learn relations that must hold over multiple parts of a configuration file.
Previous work used a set of correct configuration files as a learning set, from which it was possible to derive rules that must hold with absolute certainty\cite{santolucitoCAV}. 
However, this is approach is severely limiting. 
It is difficult to obtain a set of files that is both guaranteed to be without misconfiguration and large enough to learn the many rules of configuration files.
This usual requires manual verification of the learning set, which is prone to error.

@@

We now describe the technique we use to detect anomalous values for 
numerical attributes. Let $A$ be the set of attributes contained in the 
configuration files in the sample dataset. 
Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
values corresponding to attribute $a$, seen over the entire sample dataset.
For each $v_a$, we compute 
an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$ 
where $\hat{v_a}$ represents the median over the values 
in $v_a$ and $MAD(v_a$) refers to the 
median absolute deviation. 
This is a standard outlier detection test, namely the Hampel identifier. 
\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
for a normal distribution.} 
In the checking phase, as long as the checker finds a value for a numerical 
attribute in the checked file outside of this interval, 
a warning would be printed to the user indicating the violating value, 
the attribute, and the upper or lower Hampel threshold.

>>>>

\para{Learning from an incorrect set.}
The first step of \app is to learn relations that must hold over multiple parts of a configuration file.
Previous work used a set of correct configuration files as a learning set, from which it was possible to derive rules that must hold with absolute certainty\cite{santolucitoCAV}. 
However, this is approach is severely limiting. 
It is difficult to obtain a set of files that is both guaranteed to be without misconfiguration and large enough to learn the many rules of configuration files.
This usually requires manual verification of the learning set, which is prone to error.

@@

We now describe the technique we use to detect anomalous values for 
numerical attributes. Let $A$ be the set of attributes contained in the 
configuration files in the sample dataset. 
Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
values corresponding to attribute $a$, seen over the entire sample dataset.
For each $v_a$, we compute 
an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
where $\hat{v_a}$ represents the median over the values 
in $v_a$ and $MAD(v_a$) refers to the 
median absolute deviation. 
This is a variant of a standard outlier detection test, namely the Hampel identifier.\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
for a normal distribution.} 
In the checking phase, as long as the checker finds a value for a numerical 
attribute in the checked file outside of this interval, 
a warning would be printed to the user indicating the violating value, 
the attribute, and the upper or lower Hampel threshold.
